Submission_ResourceCount

### 2022-09-05 Submission_ResourceCount.Rmd
Reflecting on engagement variable.
new siop project

---
title: "Submission_ResourceCount"
output: pdf_document
---

@@

@@

data22$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
data22$stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
data22$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some

cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges

@@

>>>>

---
title: "Submission_ResourceCount"
output:
  pdf_document: 
    latex_engine: xelatex
---

@@

Alicia reflection 9/1/22: It actually appears that there may be more here with the engagement variable when reviewing the correlations. Knit and reflect more on the paper with that outcome being of focus.

John-o:
maybe use this as basis for another SIOP - extent to which resources and challenges are viewed similarly and also associations with engagement, burnout, etc... this operationalization is different than previous SIOP so could submit anew. Also would need a different approach to "similarity" - would need to look at item level

@@

data22$item387 <- 7-data22$item387
data22$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
data22$stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
data22$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some

@@

```{r correlation_table}
r <- corx::corx(data22[,c(405:410)],                    
                triangle = "lower",
                stars = c(0.05, 0.01, 0.001),
                describe = c(`$M$` = mean, `$SD$` = sd))

papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
                  landscape = TRUE,
                  escape = FALSE)

#cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges
